Combined single-cell transcriptomics and virus sequencing of influenza infections that trigger innate immunity

### 2018-09-17 paper/paper.tex

>>>>

\end{document}
ent}
_figures/pacbio_analysis.html}.
This notebook contains detailed descriptions of each step and plots illustrating the results, and is the best way to understand this part of the analysis in detail.
The actual Jupyter notebook rendered here is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb.}}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:monocle_analysis}
An HTML rendering of the Jupyter notebook that analyzes the annotated cell-gene matrix to generate the figures in this paper is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/single_cell_figures/monocle_analysis.html}.
This notebook contains detailed descriptions of each step and plots illustrating the results, and is the best way to understand this part of the analysis in detail.
The actual Jupyter notebook rendered here is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/monocle_analysis.ipynb.}}
\end{suppfile}

\end{document}
ent}
mlab/IFNsorted_flu_single_cell/blob/master/pacbio_analysis.ipynb.}}
\end{suppfile}

\begin{suppfile}
\caption{\label{suppfile:monocle_analysis}
An HTML rendering of the Jupyter notebook that analyzes the annotated cell-gene matrix to generate the figures in this paper is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/raw/master/paper/figures/single_cell_figures/monocle_analysis.html}.
This notebook contains detailed descriptions of each step and plots illustrating the results, and is the best way to understand this part of the analysis in detail.
The actual Jupyter notebook rendered here is available at \url{https://github.com/jbloomlab/IFNsorted_flu_single_cell/blob/master/monocle_analysis.ipynb.}}
\end{suppfile}
